Ownership types in theory and practice (in Rust)

### 2022-11-30 paper.tex
Last change before refactor of implementation in rust section

% TODO: footnote that main class etc. have been omitted for sake of simplicity
The following piece of code demonstrates how primitive values are \emph{moved} into other variables in Rust.
\begin{lstlisting}
let x: &str = "hello world";
let y: &str = x;
println!("x: {}, y: {}", x, y);
\end{lstlisting}
Since \emph{x} has a known, fixed size, its value is simply copied into \emph{y}.
Therefore, the program compiles and, as expected, "x: hello world, y: hello world" is printed to stdout.
% TODO: explain what Rust traits are
Internally, these primitive types are annotated with the \emph{Copy} trait, which specifies that

@@

>>>>

% TODO: footnote that main class etc. have been omitted for sake of simplicity
The following piece of code demonstrates how primitive values are \emph{moved} into other variables in Rust.
\begin{lstlisting}
let x: &str = "hello world";
let y: &str = x;
println!("x: {}, y: {}", x, y);
\end{lstlisting}
Since \emph{x} has a known, fixed size, its value is simply copied into \emph{y}.
Therefore, the program compiles and, as expected, "x: hello world, y: hello world" is printed to stdout.
% TODO: explain what Rust traits are
Internally, these primitive types are annotated with the \emph{Copy} trait, which specifies that variables are trivially copied instead of moved.

@@

\subsubsection{Functions and return values}

Just like a value is moved into the variable it is assigned to, a value is also moved into the function that it is passed as a parameter to.

In both case, as with variable assignment, values stored on the stack are copied instead of moved.
